Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-01 paper/snakemajoranas.tex
cite 1902.11300

\comment{The introduction of a the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
The straight system is in the symmetry class BDI \cite{pientka2017topological}.
Using the software package Qsymm~\cite{varjas2018qsymm}, we find that the zigzag shape modulation violates the chiral symmetry, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.

>>>>

\comment{The introduction of a the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
The straight system is in the symmetry class BDI \cite{pientka2017topological}.
Using the software package Qsymm~\cite{varjas2018qsymm}, we find that the zigzag shape modulation violates the chiral symmetry~\cite{1902.11300}, leaving only the particle-hole symmetry and the reflection symmetry with respect to the $x$-axis.
